Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{London version \YellowPaperVersionNumber}}

### 2023-12-07 Paper.tex
add the condition that maxPriorityFee must be less than or equal to maxFeePerGas

\begin{enumerate}
\item The transaction is well-formed RLP, with no additional trailing bytes;
\item the transaction signature is valid;
\item the \hyperlink{transaction_nonce}{transaction nonce} is valid (equivalent to the \hyperlink{account_nonce}{sender account's current nonce});
\item the sender account has no contract code deployed (see EIP-3607 by \cite{EIP-3607});
\item the gas limit is no smaller than the intrinsic gas, $g_0$, used by the transaction;
\item the sender account balance contains at least the cost, $v_0$, required in up-front payment; and
\item the \textbf{maxFeePerGas}, $T_m$, in the case of type 2 transactions, or \textbf{gasPrice}, $T_p$, in the case of type 0 and type 1 transactions, is greater than or equal to the block's base fee, $H_{\mathrm{f}}$.
\end{enumerate}

>>>>

\begin{enumerate}
\item The transaction is well-formed RLP, with no additional trailing bytes;
\item the transaction signature is valid;
\item the \hyperlink{transaction_nonce}{transaction nonce} is valid (equivalent to the \hyperlink{account_nonce}{sender account's current nonce});
\item the sender account has no contract code deployed (see EIP-3607 by \cite{EIP-3607});
\item the gas limit is no smaller than the intrinsic gas, $g_0$, used by the transaction;
\item the sender account balance contains at least the cost, $v_0$, required in up-front payment;
\item the \textbf{maxFeePerGas}, $T_m$, in the case of type 2 transactions, or \textbf{gasPrice}, $T_p$, in the case of type 0 and type 1 transactions, is greater than or equal to the block's base fee, $H_{\mathrm{f}}$; and
\item for type 2 transactions, \textbf{maxPriorityFeePerGas}, $T_f$, must be no larger than \textbf{maxFeePerGas}, $T_m$.
\end{enumerate}
